\(ler\) : LVK (LIGO-Virgo-KAGRA collaboration) event (compact-binary mergers) rate calculator and simulator

### 2024-07-01 paper/paper.tex
mac

\fancyfoot[L]{\parbox[t]{0.98\headwidth}{\footnotesize{\sffamily Phurailatpam Hemantakumar, Anupreeta More, Harsh Narola, Ng Chung Yin (Leo), Justin Janquart, Chris Van Den Broeck, Otto Akseli HANNUKSELA, Neha Singh, and David Keitel, (2024). \(ler\)
: LVK (LIGO-Virgo-KAGRA collaboration) Event (compact-binary mergers)
Rate calculator and
simulator. \textit{Journal of Open Source Software}, (), . \url{https://doi.org/10.xxxxxx/draft}}}}

@@

\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={ler : LVK (LIGO-Virgo-KAGRA collaboration) Event (compact-binary mergers) Rate calculator and simulator},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls

@@

\title{\(ler\) : LVK (LIGO-Virgo-KAGRA collaboration) Event
(compact-binary mergers) Rate calculator and simulator}

        \author[1]{Phurailatpam Hemantakumar}
          \author[2,3]{Anupreeta More}
          \author[4,5]{Harsh Narola}
          \author[1]{Ng Chung Yin (Leo)}
          \author[4,5]{Justin Janquart}
          \author[4,5]{Chris Van Den Broeck}
          \author[1]{Otto Akseli HANNUKSELA}
          \author[6]{Neha Singh}
          \author[6]{David Keitel}

      \affil[1]{Department of Physics, The Chinese University of Hong
Kong, Shatin, New Territories, Hong Kong}
      \affil[2]{The Inter-University Centre for Astronomy and
Astrophysics (IUCAA), Post Bag 4, Ganeshkhind, Pune 411007, India}
      \affil[3]{Kavli Institute for the Physics and Mathematics of the
Universe (IPMU), 5-1-5 Kashiwanoha, Kashiwa-shi, Chiba 277-8583, Japan}
      \affil[4]{Department of Physics, Utrecht University,
Princetonplein 1, 3584 CC Utrecht, The Netherlands}
      \affil[5]{Nikhef -- National Institute for Subatomic Physics,
Science Park, 1098 XG Amsterdam, The Netherlands}
      \affil[6]{Departament de F\textquotesingle isica, Universitat de
les Illes Balears, IAC3-IEEC, Crta. Valldemossa km 7.5, E-07122 Palma,
Spain}
  \date{\vspace{-7ex}}

@@

  \begin{itemize}
  \tightlist
  \item
    The calculation of rates necessitates integration over simulated
    events that meet specific detection criteria. This process includes
    computing SNRs \((\rho)\) for each event or its lensed images,
    followed by an assessment against a predetermined threshold(s)
    \((\rho_{th})\).
  \item
    SNR calculations are optimized using
    \href{https://gwsnr.readthedocs.io/en/latest/}{\emph{gwsnr}},
    leveraging interpolation and multiprocessing for accuracy and speed.
  \item
    Simulated events and rate results, along with input configurations,
    are systematically archived for easy access and future analysis.
    Additionally, all interpolators used in the process are preserved
    for future applications.
  \item
    Most cosmology-related calculations within the \emph{ler} package
    are performed using the \emph{astropy} library (Astropy
    Collaboration 2013). The default cosmological model is LambdaCDM
    (\(H_0=70,\, \Omega_m=0.3,\, \Omega_\Lambda=0.7\)); however, users
    have the flexibility to employ any cosmology available in
    \emph{astropy}. All internal calculations in \emph{ler} will then be
    based on the user-selected cosmological model.
  \end{itemize}
\end{itemize}

>>>>

\fancyfoot[L]{\parbox[t]{0.98\headwidth}{\footnotesize{\sffamily Phurailatpam Hemantakumar, Anupreeta More, Harsh Narola, Ng Chung Yin (Leo), Justin Janquart, Chris Van Den Broeck, Otto Akseli HANNUKSELA, Neha Singh, and David Keitel, (2024). \(ler\)
: LVK (LIGO-Virgo-KAGRA collaboration) event (compact-binary mergers)
rate calculator and
simulator. \textit{Journal of Open Source Software}, (), . \url{https://doi.org/10.xxxxxx/draft}}}}

@@

\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={ler : LVK (LIGO-Virgo-KAGRA collaboration) event (compact-binary mergers) rate calculator and simulator},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls

@@

\title{\(ler\) : LVK (LIGO-Virgo-KAGRA collaboration) event
(compact-binary mergers) rate calculator and simulator}

        \author[1]{Phurailatpam Hemantakumar}
          \author[2,3]{Anupreeta More}
          \author[4,5]{Harsh Narola}
          \author[1]{Ng Chung Yin (Leo)}
          \author[4,5,6,7]{Justin Janquart}
          \author[4,5]{Chris Van Den Broeck}
          \author[1]{Otto Akseli Hannukkala}
          \author[8]{Neha Singh}
          \author[8]{David Keitel}

      \affil[1]{Department of Physics, The Chinese University of Hong
Kong, Shatin, New Territories, Hong Kong}
      \affil[2]{The Inter-University Centre for Astronomy and
Astrophysics (IUCAA), Post Bag 4, Ganeshkhind, Pune 411007, India}
      \affil[3]{Kavli Institute for the Physics and Mathematics of the
Universe (IPMU), 5-1-5 Kashiwanoha, Kashiwa-shi, Chiba 277-8583, Japan}
      \affil[4]{Department of Physics, Utrecht University,
Princetonplein 1, 3584 CC Utrecht, The Netherlands}
      \affil[5]{Nikhef -- National Institute for Subatomic Physics,
Science Park, 1098 XG Amsterdam, The Netherlands}
      \affil[6]{Center for Cosmology, Particle Physics and Phenomenology
- CP3, Universit\textquotesingle e Catholique de Louvain,
Louvain-La-Neuve, B-1348, Belgium}
      \affil[7]{Royal Observatory of Belgium, Avenue Circulaire, 3, 1180
Uccle, Belgium}
      \affil[8]{Departament de F\textquotesingle isica, Universitat de
les Illes Balears, IAC3-IEEC, Crta. Valldemossa km 7.5, E-07122 Palma,
Spain}
  \date{\vspace{-7ex}}

@@

  \begin{itemize}
  \tightlist
  \item
    The calculation of rates necessitates integration over simulated
    events that meet specific detection criteria. This process includes
    computing SNRs \((\rho)\) for each event or its lensed images,
    followed by an assessment against a predetermined threshold(s)
    \((\rho_{th})\).
  \item
    SNR calculations are optimized using
    \href{https://gwsnr.readthedocs.io/en/latest/}{\emph{gwsnr}} python
    package, leveraging interpolation and multiprocessing for accuracy
    and speed.
  \item
    Simulated events and rate results, along with input configurations,
    are systematically archived for easy access and future analysis.
    Additionally, all interpolators used in the process are preserved
    for future applications.
  \item
    Most cosmology-related calculations within the \emph{ler} package
    are performed using the \emph{astropy} library (Astropy
    Collaboration 2013). The default cosmological model is LambdaCDM
    (\(H_0=70,\, \Omega_m=0.3,\, \Omega_\Lambda=0.7\)); however, users
    have the flexibility to employ any cosmology available in
    \emph{astropy}. All internal calculations in \emph{ler} will then be
    based on the user-selected cosmological model.
  \end{itemize}
\end{itemize}
